Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-10-20 crowdsource/article.tex
changes in edge orientation part

\paragraph{Edge orientation.}

Partial correlation is a symmetric measure that can not be used to predict edge
orientation. A post-processing heuristic was proposed to derive an asymmetric
association score from the partial correlation coefficient. This heuristic is
based on the observation that if there is directed edges from $i$ to $j$ then
the activation of $i$ should be followed by the activation of $j$ after a
slight delay. For every pairs $(i,j)$, we computed the following term:
\begin{align}
s_{i,j} = \sum_{t=1}^{T - 1} \mathbb{1}((x_j^{t+1} - x_i^t) \in \left[\phi_1, \phi_2\right])
\end{align}
that could be interpreted as an image of the number of times that neuron $i$
activates neuron $j$. $\phi_1$ and $\phi_2$ are parameters whose values have
been chosen equal to $0.2$ and $0.5$, respectively. The
final association score for an edge from $i$ to $j$ was
then the following:
\begin{align}
q_{i,j} = weight * p_{i,j} + (1-weight) * (s_{i,j}-s_{j,i}),
\label{eqn:qij}
\end{align}
with $p_{i,j}$ the average partial correlation coefficient and the parameter
$weight$ chosen close to 1 ($weight=0.997$). The second term is expected to be
greater (resp. lower) than 0 when $i$ more often activates $j$ than the
opposite and therefore in this case it makes $q_{i,j}$ greater (resp. lower)
than $q_{j,i}$.

\newpage
\bibliography{references}

>>>>

\paragraph{Edge orientation.}
Partial correlation is a symmetric measure that can not be used to predict edge
orientation. A post-processing heuristic was proposed to derive an asymmetric
association score from the partial correlation coefficient. This heuristic is
based on the observation that if there is directed edges from $i$ to $j$ then
the activation of $i$ should be followed by the activation of $j$ after a
slight delay. For every pairs $(i,j)$, we computed the following term:
\begin{align}
s_{i,j} = \sum_{t=1}^{T - 1} \mathbb{1}((x_j^{t+1} - x_i^t) \in \left[\phi_1, \phi_2\right])
\end{align}
where $\phi_1$ and $\phi_2$ are parameters whose values have been
optimized through experiments to $0.2$ and $0.5$, respectively. The
final association score for an edge from $i$ to $j$ was
then the following:
\begin{align}
q_{i,j} = weight * p_{i,j} + (1-weight) * (s_{i,j}-s_{j,i}),
\label{eqn:qij}
\end{align}
with $p_{i,j}$ the average partial correlation coefficient and the parameter
$weight$ optimized close to 1 ($weight=0.997$). 
\newpage
\bibliography{references}
